Web Page Visualization Code

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
did some more cleaning

```{r Load LIbraries, Directories, and Datasets}
# Load Libraries
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
library(ggplot2)
library(dplyr)
library(syuzhet)
library(sjPlot)

@@

# Merge thread relevancy scores back to thread-level dataframe
threads_summary_df <- comments_in_keyword_threads %>%
  distinct(Thread.ID, newsgroup) %>%
  left_join(thread_relevancy_scores, by = "Thread.ID")

>>>>

```{r Load Libraries, Directories, and Datasets}
# Load Libraries
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
library(ggplot2)
library(dplyr)
library(syuzhet)
library(sjPlot)

@@

# Merge thread relevancy scores with the original all_threads dataframe and filter to keep only relevant threads
threads_summary_df <- all_threads %>%
  filter(Unique_ThreadID %in% all_threads_aids$Thread.ID) %>%
  left_join(thread_relevancy_scores, by = c("Unique_ThreadID" = "Thread.ID"))

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
did some more cleaning

# Maintenance and Cleaning
```{r Reset and Setup}
rm(list = ls()) 
knitr::opts_knit$set(root.dir = '/Users/emerson/Github/usenet_AIDs_discourses_webpage')
```

```{r Import necessary R libraries}
# Load all necessary libraries at once
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
```

```{r R Define Directories and Read/Clean CSVs}
# Load Directories
output_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "combined_threads_cleaned.csv"))
all_comments <- read.csv(file.path(comments_directory, "combined_comments_cleaned.csv"))

all_threads <- all_threads %>% drop_na()
all_comments <- all_comments %>% drop_na()

@@

```{python Import necessary Python libraries}
import os
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy
```

```{python Python Define Directories and Read CSVs}
# Define directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"

# Initial Visualizations
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
plt.show()
```

@@

# Sentiment Visualizations
```{python Average Sentiment Over Time Across All Newsgroups}
import pandas as pd
import matplotlib.pyplot as plt

@@

# Network Visualizations
```{r Load R Libraries}
# Load necessary libraries
library(dplyr)
library(tidyr)
library(visNetwork)
library(igraph)  # Needed for community detection
library(RColorBrewer)  # For generating pastel colors
```

```{r Get Authors Metadata}
# Step 1: Calculate basic metadata for each author
metadata <- all_comments %>%
  group_by(Author) %>%
  summarize(
    total_threads = n_distinct(Thread.ID),  # Count distinct threads per author
    total_comments = n(),  # Total number of comments made by the author
    threads_started = sum(Thread_Relative_CommentID == "CM00001", na.rm = TRUE),  # Number of threads started by the author
    .groups = 'drop'
  )

>>>>

# Maintenance for R and Python
```{r Reset and Setup}
rm(list = ls()) 
knitr::opts_knit$set(root.dir = '/Users/emerson/Github/usenet_AIDs_discourses_webpage')
```

```{r R Load Libraries, Directories, and Datasets}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
library(visNetwork)
library(RColorBrewer)

# Load Directories
output_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "aids_related_threads.csv"))
all_comments <- read.csv(file.path(comments_directory, "aids_related_comments.csv"))
```

```{python Python Load Libraries, Directories, and Datasets}
import os
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy

# Define directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"

```{r R CSV Cleaning}
all_threads <- all_threads %>% drop_na()
all_comments <- all_comments %>% drop_na()

@@

# Initial Visualizations - Python
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
plt.show()
```

@@

# Sentiment Visualizations - Python
```{python Average Sentiment Over Time Across All Newsgroups}
import pandas as pd
import matplotlib.pyplot as plt

@@

# Network Visualizations - R
```{r Get Authors Metadata}
# Step 1: Calculate basic metadata for each author
metadata <- all_comments %>%
  group_by(Author) %>%
  summarize(
    total_threads = n_distinct(Thread.ID),  # Count distinct threads per author
    total_comments = n(),  # Total number of comments made by the author
    threads_started = sum(Thread_Relative_CommentID == "CM00001", na.rm = TRUE),  # Number of threads started by the author
    .groups = 'drop'
  )
